Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-10-10 ms.tex
idle versus exposing test

\clearpage
\subsection{Noise floor}

>>>>

\subsection{Idle versus exposing residuals}
The current loads on the asics are different when they are in idle mode (resetting and not collecting data) versus exposing (collecting reads up the ramps).
We induced a higher load on detector 487 on purpose by running a $\sim$ 3 hour exposure while the remaining detectors ran in idle mode.
We then started an exposure with all 4 detectors to see if detector 487 exhibited a different time series than the remaining 3 detectors.
The result shown in Figure \ref{fig:idleVersusExposing320}.
\begin{figure*}
\gridline{
\fig{individual_azlab06_sub320_idle_vs_exp.pdf}{0.49\textwidth}{Data collection versus idle reset}
}
\caption{The time series of the AZLab 06 $320 \times 320$ subarrays on all four detectors look the same for the first hour even though detector 487 had a higher current draw 3 hours preceding the exposure because it had a higher current draw.}\label{fig:idleVersusExposing320}
\end{figure*}

\subsection{Noise floor}
